### 2018-12-29 papers/journal/experiments.tex
update of exper

\subsection{Implementation}
{\sattool} is based on the architecture of a bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.
%
{\smttool} is based on the SMT solver Z3 and uses the efficient encoding of finding a least fixed point to solve reachability problem. 
%
{\qbftool} is based on the QBF encoding of the universal condition and uses {\depqbf} solver to solve the generated QBF. 
%
The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS using {\qbftool}.
%
All the experiments were done on a machine with  Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM with 30 min (1800 sec) timeout.

>>>>

\subsection{Implementation}
%The existential condition is implemented with two different encodings. First, with a bounded model checker that uses an enumeration of paths for encoding the reachability problem: {\sattool}.
%which is based on the architecture of a
%
%The other with an SMT solver Z3 that uses the efficient encoding of finding a least fixed point to solve it: {\smttool}.
{\sattool} is based on the architecture of a bounded model checker (CBMC) and uses an enumeration of paths for encoding the reachability problem.
%
{\smttool} is based on the SMT solver Z3 and uses the efficient encoding of finding a least fixed point to solve reachability problem. 
%
{\qbftool} is based on the QBF encoding of the universal condition and uses {\depqbf} solver to solve the generated QBF. 
%
The {\ourtool} is a synthesis tool for synthesizing incomplete information in the input VTS using {\qbftool}.
%
All the experiments were done on a machine with  Intel(R) Core(TM) i7-2600 CPU @ 3.40GHz processor and 16GB RAM with 30 min (1800 sec) timeout.
